### 2022-06-01 paper.tex
add workflow figure

Lukas P. M. Kremer, Leonie Küchenhoff, ..., Simon Anders\\
{\footnotesize University of Heidelberg, Germany}
\vspace{1.5ex}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/Fig_sliding.png}
	\caption{\small \textbf{Finding variably methylated regions (VMR):} The chromosomes are divided up into overlapping windows (first five shown at the bottom), and for each window, the cells' methylation values are calculated as described and as depicted in Fig.\ \ref{smoothres}B. Then, the variance of these values are calculated (each point represents one of the overlapping windows), a threshold (red line) is chosen such that a chosen quantile of windows have a variance exceeding the threshold. Windows with above-threshold variance are merged if they overlap, yielding the ``variably methylated regions''.}
	\label{vmr}
\end{figure}

@@

We have implemented the approach just described in a Python package, called ``scbs'', that offers the following functionality:

@@

The function `scbs prepare` reads a set of CpG coverage files (e.g. produced by Bismark) and produces a file that stores the matrix $x$ in a space-efficient format, as follows: $x$ is represented as a NumPy sparse matrix, encoding the actual values 0, 1, and NA as -1, 1, and 0, respectively. Coding NA (the most common value) as 0 leverages NumPy's sparse matrix storage. In all the follows here, any mention of $x$ will, however, always mean the encoding as $x_{ij}\in\{0,1,\text{NA}\}$.

>>>>

Lukas P.~M. Kremer, Leonie Küchenhoff, Santiago Cerrizuela, ..., Ana Martin-Villalba, Simon Anders\\
{\footnotesize University of Heidelberg, Germany}
\vspace{1.5ex}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/Fig_sliding.png}
	\caption{\small \textbf{Finding variably methylated regions (VMR):} The chromosomes are divided up into overlapping windows (first five shown at the bottom), and for each window, the cells' methylation values are calculated as described and as depicted in Fig.\ \ref{smoothres}B. Then, the variance of these values is calculated (each point represents one of the overlapping windows), a threshold (dashed line) is chosen such that a chosen quantile of windows have a variance exceeding the threshold. Windows with above-threshold variance are merged if they overlap, yielding the ``variably methylated regions''.}
	\label{vmr}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/Fig_workflow.png}
	\caption{\small \textbf{Overview of the functionalities implemented in the scbs package} Bla bla.}
	\label{workflow}
\end{figure}

We have implemented the approach just described in a Python package, called ``scbs'', that offers the following functionality \ref{workflow}:

@@

The function `scbs prepare` reads a set of CpG coverage files (e.g. produced by Bismark) and produces a file that stores the matrix $x$ in a space-efficient format, as follows: $x$ is represented as a SciPy sparse matrix, encoding the actual values 0, 1, and NA as -1, 1, and 0, respectively. Coding NA (the most common value) as 0 leverages SciPy's sparse matrix storage. In all the follows here, any mention of $x$ will, however, always mean the encoding as $x_{ij}\in\{0,1,\text{NA}\}$.
